### 2018-08-03 article.tex
Q-valued rewriting systems: Proposition 2

\begin{itemize}
\item 0-cells are natural number $\mathbb{N}$
\item 1-cells are quantum circuits freely generated by $\circ$, $\otimes$ and $\{f_i\}_i$, a set of quantum circuits
\item 2-cells are quantum circuit transformations freely generated by $\circ$, $\otimes$ and $\{r_i\}_i$, a set of ransformations, such that $\forall r: f \Rightarrow g \in \{r_i\}_i, \exists r^{-1}: g \Rightarrow f \in \{r_i\}_i$
\[
r \circ r^{-1} = id_f
\]
\item the vertical composition is the usual transformations composition
\item the horizontal composition is the usual circuits composition
\item the 2-bifunctor is
\begin{itemize}
\item on 0-cell, $a \otimes b = a + b$
\item on $\catC(a, b)$, a functor $C(a, b) \otimes C(a', b') \to C(a + a', b + b')$
\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two transformations $r, s: f \Rightarrow g$, then $F(r) = F(s)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION CO           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformations $r: f \Rightarrow g$, then $F(r) = F(f) \oplus F(g)^{-1}$.
Note that the definition of $F$ gives that only for $r \in \{f_i\}_i$.
\end{corollary}

>>>>

\begin{itemize}
\item 0-cells are natural number $\mathbb{N}$
\item 1-cells are quantum circuits freely generated by $\circ$, $\otimes$ and $\{f_i\}_i$, a set of quantum circuits
\item 2-cells are quantum circuit transformations freely generated by $\circ$, $\otimes$ and $\{r_i\}_i$, a set of ransformations, such that $\forall r: f \Rightarrow g \in \{r_i\}_i, \exists r^{-1}: g \Rightarrow f \in \{r_i\}_i$
\[
r \circ r^{-1} = id_f
\]
\item the vertical composition is the usual transformations composition
\item the horizontal composition is the usual circuits composition
\item the 2-bifunctor is
\begin{itemize}
\item on 0-cell, $a \otimes b = a + b$
\item on $\catC(a, b)$, a functor $\catC(a, b) \otimes C(a', b') \to C(a + a', b + b')$
\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
Given two transformations $r, s: f \Rightarrow g$, then $F(r) = F(s)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 1 COROLLARY        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{corollary}
For all transformations $r: f \Rightarrow g$, then $F(r) = F(f) \oplus F(g)^{-1}$.
Note that the definition of $F$ gives that only for $r \in \{f_i\}_i$.
\end{corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
The following category $\catC(\mathbb{Q})$ is a $\mathbb{Q}$-category
\begin{itemize}
\item A set of objects which are the 1-cells of $\catC$
\item For all objects $(f, g)$
\end{itemize}
\[
\catE(f, g) = \begin{cases} {\rm if~} f \Rightarrow g \in \catC, &F(f \Rightarrow g) \cr {\rm otherwise~} &\top \end{cases}
\]
With $\top \in Q$ such that for all $x \in \mathbb{Q}$
\[
x \preceq \top
\]

\begin{proof}
For all 1-cells $(f, g)$, if it exists a unique transformation $f \Rightarrow g$, then
\begin{align}
\catE(f, g) &= F(f \Rightarrow g) \in \mathbb{Q} \cr
&= F(f) \oplus F(g)^{-1}
\end{align}
otherwise we already have $\catE(f, g) = \top \in \mathbb{Q}$.
For all 1-cell $f$, we know that there is a identity transformation $f \Rightarrow f$ and
\begin{align}
\catE(f, f) &= F(id_f) \cr
&= F(f \Rightarrow f)\cr
&= F(f) \oplus F(f)^{-1} \cr
&= e
\end{align}
Finally, for all 1-cells $(f, g, h)$ such that there exists $r: f \Rightarrow g$ and $s: g \Rightarrow h$ in $\catC$, then the homomorphism $F$ give us
\begin{align}
\catE(f, h) &= F(f \Rightarrow h) \cr
&= F(s\circ r) \cr
&= F(s) \oplus F(r) \cr
&= F(g \Rightarrow h) \oplus F(f \Rightarrow g) \cr
&= \catE(g, h) \oplus \catE(f, g)
\end{align}
If either $r$ or $s$ doesn't exists in $\catC$ then
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]
become
\[\begin{matrix}
&\catE(b, c) \oplus \top &\succeq \top \cr
{\rm or~} &\top \oplus \catE(a, b) &\succeq \top \cr
{\rm or~} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}
